---
title: "Plinko Online Analysis"
author: "Tobias Gerstenberg, Joseph Outa, Xi Jia Zhou"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

# SETUP

## Load libraries

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library("readxl")      # for reading excel files 
library("png")         # for adding images to ggplot 
library("egg")         # for geom_custom()
library("grid")        # functions for dealing with images 
library("ggpubr")      # for plotting
library("knitr")       # for knitting
library("janitor")     # for cleaning column names 
library("transport")   # for computing Wasserstein distance
library("kableExtra")  # for knitr tables
library("xtable")      # for latex tables
library("patchwork")   # for figure panels
library("corrr")       # for correlations
library("broom.mixed") # for tidying up regression results
library("emmeans")     # for regression follow ups 
library("boot")        # for the inverse logit function
library("tidyverse")   # for wrangling and plotting 
library("brms")        # for Bayesian data analysis
```

## Set options

```{r, echo=FALSE}
theme_set(theme_classic() + 
    theme(text = element_text(size = 24)))

opts_chunk$set(comment = "",
               fig.show = "hold")

options(dplyr.summarise.inform = F)

# function for printing out html or latex tables 
print_table = function(data, format = "html", digits = 2){
  if(format == "html"){
    data %>% 
      kable(digits = digits) %>% 
      kable_styling()
  }else if(format == "latex"){
    data %>% 
      xtable(digits = digits) %>%
      print(include.rownames = F,
            booktabs = T)
  }
}
```

# DATA 

## Load and structure data

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# trial information from the adult plinko eye-tracking experiment 
load("data/selection.RData")

# posterior distributions for the different models 
load("data/posterior.RData")

# load data from adult participants 
load("data/judgments.RData")

# raw data 
df.data = read_excel(path = "../../data/plinko_online_experiment.xlsx",
                     sheet = "sheet1") %>% 
  clean_names() %>% 
  filter(exclude == "no") %>% 
  mutate(participant = 1:n()) %>% 
  relocate(participant)
    
# demographics 
df.demographics = df.data %>% 
  select(participant, child_id, age, gender, race, condition,
         sound_familiarization, practice_drops)

# participants' choices 
df.choices = df.data %>% 
  select(participant, age, condition, contains("resp")) %>% 
  pivot_longer(cols = starts_with("resp"),
               names_to = "trial",
               values_to = "answer") %>% 
  mutate(answer = case_when(answer == "green" ~ "3",
                            answer == "yellow" ~ "2",
                            answer == "blue" ~ "1")) %>% 
  mutate(trial = as.numeric(str_remove(trial, "resp_trial"))) %>% 
  left_join(read_csv("../../data/plinko_online_experiment_counterbalance.csv",
                     show_col_types = FALSE),
            by = c("condition", "trial")) %>% 
  mutate(across(c("condition", "answer", "world"),
                ~ as.numeric(.)))

df.choices = df.choices %>% 
  left_join(df.judgments %>% 
              rename(world = trial,
                     ground_truth = hole) %>% 
              filter(world %in% df.choices$world) %>% 
              distinct(world, ground_truth),
            by = "world") %>% 
  mutate(correct = ifelse(answer == ground_truth, 1, 0)) %>% 
  na.omit()
```

## Add model predictions 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# x positions of the holes
hole_positions = c(151.229172, 300, 448.770844)

df.model = df.choices %>% 
  distinct(world) %>% 
  left_join(df.selection %>% 
              select(world, hole, x),
            by = "world") %>% 
  left_join(df.posterior %>% 
              select(world, hole, contains("_loss"), contains("entropy")),
            by = c("world", "hole")) %>% 
  rename_with(.fn = ~ str_remove(., "loss_")) %>% 
  rename_with(.fn = ~ str_replace(., "combined", "both")) %>% 
  mutate(across(contains("hole"), .fns = ~ . * 100),
         world_order = rank(entropy_both,
                            ties.method = "first")) %>% 
  select(world, world_order, contains("hole"),
         entropy_vision, entropy_sound, entropy_both, -hole) %>% 
  arrange(world_order)

# fit parameter for matching model
fun_fit_matching_sd = function(sd_matching){
    df.choices %>% 
        left_join(df.selection %>% 
                      select(world, x),
                  by = "world") %>% 
        mutate(matching = dnorm(x - hole_positions,
                                sd = sd_matching,
                                log = T)) %>% 
        summarize(likelihood = -sum(matching)) %>% 
        pull(likelihood)
}

sd_optimal = optim(par = 1,
                   fn = fun_fit_matching_sd)

df.predictions = df.model %>% 
  pivot_longer(cols = contains("hole"),
               names_to = c("answer", "model"),
               names_sep = "_",
               values_to = "prediction") %>% 
  mutate(answer = str_remove(answer, "hole"),
         answer = factor(answer, levels = 1:3),
         prediction = prediction / 100) %>% 
  pivot_wider(names_from = model,
              values_from = prediction) %>% 
  mutate(baseline = 1/3) %>% 
  left_join(df.selection %>% 
              select(world, x),
            by = "world") %>% 
  group_by(world) %>% 
  mutate(matching = dnorm(x - hole_positions, sd = sd_optimal$par),
         matching = matching / sum(matching)) %>% 
  select(-x)

# add adult means to model predictions 
df.adults = df.choices %>% 
  distinct(world) %>% 
  left_join(df.judgments %>% 
              rename(world = trial) %>% 
              select(experiment,
                     world,
                     participant,
                     answer = response,
                     ground_truth = hole),
            by = "world")

df.predictions = df.predictions %>% 
  left_join(df.adults %>% 
              mutate(answer = factor(answer, levels = 1:3)) %>% 
              count(experiment, world, answer,
                    .drop = F) %>% 
              group_by(experiment, world) %>% 
              mutate(p = n / sum(n),
                     experiment = str_c("adult_", experiment)) %>% 
              ungroup() %>% 
              select(-n) %>% 
              pivot_wider(names_from = experiment, 
                          values_from = p),
            by = c("world", "answer")) %>% 
  ungroup()

```

# STATS 

## Trial selection 

```{r, echo=FALSE, eval=FALSE}
hole_positions = c(151.229172, 300, 448.770844)

selection = c(91, 31, 32, 94, 35, 149, 62, 143, 19)

df.trial_selection  = df.judgments %>% 
  mutate(response = factor(response, levels = 1:3)) %>% 
  count(experiment, trial, hole, response, .drop = F) %>% 
  pivot_wider(names_from = experiment, 
              values_from = n) %>% 
  group_by(trial, hole) %>% 
  mutate(vision_max = which.max(vision),
         vision_sound_max = which.max(vision_sound)) %>% 
  group_by(trial, hole, vision_max, vision_sound_max) %>% 
  mutate(across(c(vision, vision_sound), ~ . / sum(.))) %>% 
  summarize(distance = wasserstein1d(vision, vision_sound, p = 2)) %>% 
  arrange(desc(distance)) %>% 
  left_join(df.selection %>% 
              select(trial = world, x, ncollisions) %>% 
              rowwise() %>% 
              mutate(matching_max = which.min(abs(x - hole_positions))),
            by = "trial") %>% 
  relocate(matching_max, .after = vision_sound_max) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(n_different = length(unique(c_across(contains("_max")))))

df.trial_selection %>%   
  filter(trial %in% selection) %>% 
  select(-x) %>% 
  print_table()
```

## Fit separate models to each participant 

### Children

```{r}
# adult data 
# model_selection = c("adult_vision", "adult_vision_sound", "baseline", "matching")

# computational models 
model_selection = c("vision", "both", "baseline", "matching")

df.fits = df.choices %>% 
  mutate(answer = factor(answer, levels = 1:3)) %>% 
  left_join(df.predictions %>% 
              select(world, answer, all_of(model_selection)),
            by = c("world", "answer")) %>% 
  mutate(across(all_of(model_selection), ~ ifelse(. == 0, 0.01, .))) %>% 
  group_by(age, participant) %>% 
  summarize(across(all_of(model_selection), ~ exp(sum(log(.))))) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(sum = sum(c_across(all_of(model_selection))),
         across(all_of(model_selection), ~ . / sum)) %>% 
  select(-sum)
```

### Adults 

- maybe the matching model should be fit separately for adults (and for the selection of trials?!)

```{r}
# model_selection = c("adult_vision", "adult_vision_sound", "baseline", "matching")

# computational models 
model_selection = c("vision", "both", "baseline", "matching")

df.fits.adults = df.adults %>% 
    mutate(answer = as.factor(answer)) %>% 
    filter(world %in% unique(df.choices$world)) %>% 
    left_join(df.predictions %>% 
                  select(world, answer, all_of(model_selection)),
              by = c("world", "answer")) %>% 
    mutate(across(all_of(model_selection), ~ ifelse(. == 0, 0.01, .))) %>% 
    group_by(experiment, participant) %>% 
    summarize(across(all_of(model_selection), ~ exp(sum(log(.))))) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(sum = sum(c_across(all_of(model_selection))),
           across(all_of(model_selection), ~ . / sum)) %>% 
    select(-sum)
```

## Correlation between models 

```{r message=FALSE, warning=FALSE}
df.predictions %>% 
    select(matching, vision, both) %>% 
    # correlate(method = "spearman") %>% 
    correlate() %>% 
    shave() %>% 
    fashion()
```

## Accuracy as a function of age 

```{r}
df.choices %>% 
    mutate(age = as.character(age)) %>% 
    group_by(age) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    bind_rows(df.adults %>% 
                  filter(experiment == "vision_sound") %>% 
                  mutate(correct = answer == ground_truth) %>% 
                  summarize(pct_correct = sum(correct)/n()) %>% 
                  mutate(age = "adult",
                         .before = pct_correct)) %>% 
    print_table()
```

## Multinomial regression 

- tests whether the distribution of answers changes with age 
- Note: this analysis doesn't make too much sense as one wouldn't expect that 1, 2, or 3 answers in general change with age ... 

```{r}
df.stat = df.choices %>% 
    select(participant, age, trial, answer) %>% 
    mutate(answer = as.factor(answer))

fit.age_answer = brm(formula = answer ~ 1 + age + (1 | participant),
    data = df.stat,
    family = categorical(),
    seed = 1,
    file = "cache/fit.age_answer")
```

## Logistic regressions

### Effect of age 

- tests whether the probability of being correct changes with age 

```{r}
df.stat = df.choices %>% 
    select(participant, age, trial, correct)

fit.age_correct = brm(formula = correct ~ 1 + age + (1 | participant),
    data = df.stat,
    family = "bernoulli",
    seed = 1,
    file = "cache/fit.age_correct")

fit.age_correct
```

### 7s and 8s above chance (33%)? 

```{r}
# 7 year olds
df.stat = df.choices %>% 
    select(participant, age, trial, correct) %>% 
    filter(age == 7)

fit.seven_correct = brm(formula = correct ~ 1 + (1 | participant),
    data = df.stat,
    family = "bernoulli",
    seed = 1,
    file = "cache/fit.seven_correct")

# 8 year olds
df.stat = df.choices %>% 
    select(participant, age, trial, correct) %>% 
    filter(age == 8)

fit.eight_correct = brm(formula = correct ~ 1 + (1 | participant),
    data = df.stat,
    family = "bernoulli",
    seed = 1,
    file = "cache/fit.eight_correct")

# results (in probability scale)
fit.seven_correct %>% 
    tidy() %>% 
    filter(effect == "fixed") %>% 
    select(estimate, contains("conf")) %>% 
    mutate(across(.cols = everything(),
                  .fns = ~ inv.logit(.)))

fit.eight_correct %>% 
    tidy() %>% 
    filter(effect == "fixed") %>% 
    select(estimate, contains("conf")) %>% 
    mutate(across(.cols = everything(),
                  .fns = ~ inv.logit(.)))
```


## Probability of different strategies for different age ranges 

```{r}
df.fits %>% 
    ungroup() %>% 
    filter(age < 6) %>% 
    summarize(matching = mean(matching))

df.fits %>% 
    ungroup() %>% 
    filter(age < 6) %>% 
    summarize(simulation = mean(vision) + mean(both))

df.fits %>% 
    ungroup() %>% 
    filter(age == 3) %>% 
    summarize(guessing = mean(baseline))

df.fits %>% 
    ungroup() %>% 
    filter(age >= 6) %>% 
    summarize(simulation = mean(vision) + mean(both))

df.fits %>% 
    ungroup() %>% 
    filter(age == 8) %>% 
    summarize(simulation = mean(both))
```


# PLOTS 

## Participant age 

```{r fig.height=4, fig.width=6, echo=FALSE}
ggplot(data = df.data %>% 
         mutate(age = as.factor(age)),
       mapping = aes(x = age, 
                     fill= age)) + 
  geom_bar(stat = "count",
           color = "black") +
  geom_text(mapping = aes(label = stat(count)),
            stat = "count",
            nudge_y = 0.5,
            size = 5) +
    labs(x = "years", 
       y = "number") +
  scale_fill_brewer(palette = "Greens") +
  theme(legend.position = "none")

ggsave(filename = "../../figures/plots/age_distribution.pdf",
       width = 8,
       height = 6)
```

## Participant gender

```{r fig.height=4, fig.width=6, echo=FALSE}
ggplot(data = df.data, 
       mapping = aes(x = gender,
                     fill = gender)) +
    geom_bar() +
    geom_text(aes(label = stat(count)),
              stat = 'count',
              nudge_y = 0.5,
              size = 5) +
    labs(y = "Number") +
    scale_fill_brewer(palette = "Set1") +
    theme(legend.position = "none") 
```

## Answers per world 

### Function to create plot with images 

```{r, echo=FALSE}
func_plot_with_images = function(data, model){
  
  df.plot = data %>% 
    mutate(answer = factor(answer, levels = 1:3)) %>% 
    count(world, ground_truth, answer, .drop = F) %>% 
    group_by(world) %>% 
    mutate(p = n / sum(n)) %>% 
    mutate(correct = ground_truth == answer) %>% 
    ungroup()
  
  df.plot.model = model %>% 
    select(world, answer, vision, both) %>% 
    pivot_longer(cols = c(vision, both),
                 names_to = "model",
                 values_to = "prediction") %>% 
    filter(model %in% c("vision", "both"))
  
  func_load_image = function(world){
    readPNG(str_c("../../stimuli/images/study/test/world_", world, "_final.png"))
  }
  
  # linking images and worlds
  df.images = df.plot %>%
    distinct(world) %>%
    arrange(world) %>%
    mutate(grob = map(.x = world,
                      .f = ~ func_load_image(world = .x)))
  
  # plotting
  p = ggplot(data = df.plot,
             mapping = aes(x = answer,
                           y = p)) +
    geom_col(mapping = aes(fill = answer,
                           size = correct),
             alpha = 0.75,
             color = "black",
             show.legend = F) +
    geom_point(data = df.plot.model,
               mapping = aes(x = answer,
                             y = prediction,
                             shape = model,
                             group = model),
               position = position_dodge(width = 0.5),
               size = 3) +
    geom_hline(yintercept = 1/3,
               linetype = 2) + 
    geom_custom(data = df.images,
                mapping = aes(data = grob,
                              x = -Inf,
                              y = Inf),
                grob_fun = function(x) rasterGrob(x,
                                                  interpolate = T,
                                                  vjust = -0.05,
                                                  hjust = 0)) +
    facet_wrap(~ world, 
               nrow = 1) +
    labs(y = "proportion %") + 
    scale_size_manual(values = c(0.5, 1.5)) + 
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = seq(0, 100, 25),
                       limits = c(0, 1),
                       expand = expansion(add = c(0, 0))) +
    # scale_x_continuous(breaks = 1:3,
    #                    labels = 1:3,
    #                    limits = c(0, 4)) + 
    coord_cartesian(clip = "off") +
    theme(panel.grid.major.y = element_line(),
          axis.text.y = element_text(size = 25),
          axis.text.x = element_text(size = 25),
          axis.title = element_blank(),
          strip.background = element_blank(),
          strip.text = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          panel.spacing.x = unit(0.5, "cm"),
          plot.margin = margin(t = 5, l = 1, r = 0.2, b = 0, unit = "cm"))
  return(p)
}
```


### Model predictions (one row)

```{r fig.height=5, fig.width=22}

models = c("baseline", "matching", "vision", "both")
models = c("baseline", "matching", "adult_vision", "adult_vision_sound")

df.plot = df.predictions %>% 
    select(world, answer, all_of(models)) %>% 
    pivot_longer(cols = -c(world, answer),
                 names_to = "model",
                 values_to = "prediction") %>% 
    filter(model %in% models) %>% 
    mutate(model = factor(model,
                          levels = models,
                          # labels = c("guessing", "matching", "vision", "vision & sound")))
                          labels = c("guessing", "matching",
                                     "simulation (vision)","simulation (vision & sound)")))

func_load_image = function(world){
    readPNG(str_c("../../figures/ground_truth/trial_", world, ".png"))
}

# linking images and worlds
df.images = df.plot %>%
    distinct(world) %>%
    arrange(world) %>%
    mutate(grob = map(.x = world,
                      .f = ~ func_load_image(world = .x)))

df.text = df.plot %>% 
    distinct(world) %>% 
    arrange(world) %>% 
    mutate(index = 1:n(),
           x = 0.8,
           y = Inf)
  
# plotting
p = ggplot(data = df.plot,
           mapping = aes(x = answer,
                         y = prediction)) +
    geom_col(mapping = aes(fill = model,
                           group = model),
             position = position_dodge(width = 0.9),
             color = "black") +
    geom_hline(yintercept = 1/3,
               linetype = 2) + 
    geom_custom(data = df.images,
                mapping = aes(data = grob,
                              x = -Inf,
                              y = Inf),
                grob_fun = function(x) rasterGrob(x,
                                                  interpolate = T,
                                                  vjust = -0.05,
                                                  hjust = 0)) +
    geom_text(data = df.text,
              mapping = aes(x = x,
                            y = y,
                            label = index),
              size = 12,
              color = "white",
              vjust = -4) + 
    facet_wrap(~ world, 
               nrow = 1) +
    labs(y = "proportion %") + 
    scale_size_manual(values = c(0.5, 1.5)) + 
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = str_c(seq(0, 100, 25), "%"),
                       limits = c(0, 1),
                       expand = expansion(add = c(0, 0))) +
    coord_cartesian(clip = "off") +
    scale_fill_brewer(palette = "Set1") + 
    theme(panel.grid.major.y = element_line(),
          axis.text.y = element_text(size = 25),
          axis.text.x = element_text(size = 25),
          axis.title = element_blank(),
          legend.position = "bottom",
          strip.background = element_blank(),
          strip.text = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          panel.spacing.x = unit(0.5, "cm"),
          plot.margin = margin(t = 5, l = 1, r = 0.2, b = 0, unit = "cm"))
p

ggsave(filename = "../../figures/plots/model_predictions_adults.pdf",
# ggsave(filename = "../../figures/plots/model_predictions_models.pdf",
       width = 22,
       height = 5)
```

### Model predictions (3x3)

```{r fig.height=18, fig.width=10, eval=FALSE}
df.plot = df.predictions %>% 
    select(world, answer, baseline, matching, vision, both) %>% 
    pivot_longer(cols = c(baseline, matching, vision, both),
                 names_to = "model",
                 values_to = "prediction") %>% 
    filter(model %in% c("baseline", "matching", "vision", "both")) %>% 
    mutate(model = factor(model,
                          levels = c("baseline", "matching", "vision", "both"),
                          labels = c("baseline", "matching", "vision", "vision & sound")))

func_load_image = function(world){
    readPNG(str_c("../../figures/ground_truth/trial_", world, ".png"))
}

# linking images and worlds
df.images = df.plot %>%
    distinct(world) %>%
    arrange(world) %>%
    mutate(grob = map(.x = world,
                      .f = ~ func_load_image(world = .x)))
  
  # plotting
p = ggplot(data = df.plot,
           mapping = aes(x = answer,
                         y = prediction)) +
    geom_col(mapping = aes(fill = model,
                           group = model),
             position = position_dodge(width = 0.9),
             color = "black") +
    geom_hline(yintercept = 1/3,
               linetype = 2) + 
    geom_custom(data = df.images,
                mapping = aes(data = grob,
                              x = -Inf,
                              y = Inf),
                grob_fun = function(x) rasterGrob(x,
                                                  interpolate = T,
                                                  vjust = -0.05,
                                                  hjust = 0)) +
    facet_wrap(~ world, 
               nrow = 3) +
    labs(y = "proportion %") + 
    scale_size_manual(values = c(0.5, 1.5)) + 
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = str_c(seq(0, 100, 25), "%"),
                       limits = c(0, 1),
                       expand = expansion(add = c(0, 0))) +
    coord_cartesian(clip = "off") +
    scale_fill_brewer(palette = "Set1") + 
    theme(panel.grid.major.y = element_line(),
          axis.text.y = element_text(size = 25),
          axis.text.x = element_text(size = 25),
          axis.title = element_blank(),
          legend.position = "bottom",
          strip.background = element_blank(),
          strip.text = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          panel.spacing.x = unit(0.5, "cm"),
          panel.spacing.y = unit(6.5, "cm"),
          plot.margin = margin(t = 6.5, l = 1, r = 0.2, b = 0, unit = "cm"))
p

ggsave(filename = "../../figures/plots/model_predictions_3by3.pdf",
       width = 10,
       height = 18)
```


### Children

#### Overall

```{r fig.height=5, fig.width=20, echo=FALSE}
func_plot_with_images(data = df.choices,
                      model = df.predictions)
```

#### Separated by age 

```{r fig.height=25, fig.width=20}
# p1 = func_plot_with_images(data = df.choices %>% 
#                              filter(age == 3),
#                            model = df.predictions)

p1 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 3),
                           model = df.predictions)

p2 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 4),
                           model = df.predictions)

p3 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 5),
                           model = df.predictions)

p4 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 6),
                           model = df.predictions)

p5 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 7),
                           model = df.predictions)

p6 = func_plot_with_images(data = df.choices %>% 
                             filter(age == 8),
                           model = df.predictions)
p1 + p2 + p3 + p4 + p5 + p6 + 
  plot_layout(ncol = 1,
              tag_level = "new") + 
  plot_annotation(tag_levels = "A")
```



### Adults (Vision only)

```{r fig.height=5, fig.width=20, echo=FALSE}
func_plot_with_images(data = df.adults %>% 
                        filter(experiment == "vision"),
                      model = df.predictions)
```

### Adults (Vision & Sound)

```{r fig.height=5, fig.width=20, echo=FALSE}
func_plot_with_images(data = df.adults %>% 
                        filter(experiment == "vision_sound"),
                      model = df.predictions)
```

## Accuracy with age (discrete)

```{r fig.height=4, fig.width=7}
set.seed(1)

df.plot = df.choices %>% 
    # mutate(age = str_c(age, "yo")) %>% 
    mutate(age = as.character(age)) %>% 
    group_by(participant, age) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    bind_rows(df.adults %>% 
                  filter(experiment == "vision_sound") %>% 
                  mutate(correct = answer == ground_truth,
                         age = "adult") %>% 
                  group_by(participant, age) %>% 
                  summarize(pct_correct = sum(correct)/n())) %>% 
    ungroup() %>% 
    mutate(age = as.factor(age))

df.text = df.plot %>%
    distinct(age, participant) %>%
    count(age) %>%
    mutate(label = n,
           label = ifelse(age == 3, str_c("n = ", n), n),
           y = 0.95)

ggplot(data = df.plot,
       mapping = aes(x = age,
                     y = pct_correct)) + 
    geom_hline(yintercept = seq(0, 1, 0.1),
               linetype = 1,
               alpha = 0.1) + 
    geom_hline(yintercept = 1/3,
               linetype = 2,
               color = "gray50") + 
    stat_summary(fun.data = "mean_cl_boot",
                 size = 1) +
    geom_text(data = df.text,
              mapping = aes(x = age,
                            y = y,
                            label = label),
              size = 6,
              color = "gray20") +
    labs(x = "age group",
         y = "% correct") +
    coord_cartesian(ylim = c(0, 1)) + 
    scale_y_continuous(breaks = seq(0, 1, 0.2),
                       labels = str_c(seq(0, 1, 0.2) * 100, "%"),
                       expand = expansion(add = c(0, 0.05)))
    
ggsave(filename = "../../figures/plots/points_accuracy.pdf",
       width = 7,
       height = 4)
```

## Accuracy with age (continuous)

```{r fig.height=4, fig.width=7}
set.seed(1)

df.plot.individual = df.choices %>% 
    # add continuous age
    left_join(df.data %>% 
                  select(participant, age_cts),
              by = "participant") %>% 
    group_by(participant, age, age_cts) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    ungroup() %>% 
    mutate(age = factor(age, levels = c(3:8, "adult")))

df.plot.means = df.choices %>% 
    mutate(age = as.character(age)) %>% 
    group_by(participant, age) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    bind_rows(df.adults %>% 
                  filter(experiment == "vision_sound") %>% 
                  mutate(correct = answer == ground_truth,
                         age = "adult") %>% 
                  group_by(participant, age) %>% 
                  summarize(pct_correct = sum(correct)/n())) %>% 
    group_by(age) %>% 
    summarize(response = Hmisc::smean.cl.boot(pct_correct),
              n = n()) %>% 
    mutate(index = c("mean", "low", "high")) %>% 
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
    left_join(df.choices %>% 
                  left_join(df.data %>% 
                                select(participant, age_cts),
                            by = "participant") %>% 
                  distinct(participant, age, age_cts) %>% 
                  group_by(age) %>% 
                  summarize(age_mean = mean(age_cts)) %>% 
                  mutate(age = as.character(age)),
              by = "age") %>% 
    mutate(age_mean = ifelse(age == "adult", 10, age_mean),
           age = factor(age, levels = c(3:8, "adult")))

df.text = df.plot.means %>% 
    select(age, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age == "3", str_c("n = ", n), n),
           y = 0.95)

ggplot() + 
    geom_hline(yintercept = seq(0, 1, 0.1),
               linetype = 1,
               alpha = 0.1) + 
    geom_hline(yintercept = 1/3,
               linetype = 2,
               color = "gray50") + 
    geom_point(data = df.plot.individual,
               mapping = aes(x = age_cts,
                             y = pct_correct,
                             color = age),
               show.legend = F,
               size = 1) +
    geom_pointrange(data = df.plot.means,
                    mapping = aes(x = age_mean,
                                  y = mean,
                                  ymin = low,
                                  ymax = high,
                                  fill = age),
                    shape = 21,
                    size = 1,
                    show.legend = F) +
    geom_text(data = df.text,
              mapping = aes(x = age_mean,
                            y = y,
                            label = label),
              size = 6,
              color = "gray20") +
    labs(x = "age (in years)",
         y = "% correct") +
    coord_cartesian(ylim = c(0, 1)) + 
    scale_x_continuous(breaks = c(seq(3, 9, 1), 10),
                       labels = c(seq(3, 9, 1), "adults"),
                       expand = expansion(add = c(0.2, 0.5))) + 
    scale_y_continuous(breaks = seq(0, 1, 0.2),
                       labels = str_c(seq(0, 1, 0.2) * 100, "%"),
                       expand = expansion(add = c(0, 0.05))) + 
    scale_fill_brewer(type = "qual", palette = 2) +
    scale_color_brewer(type = "qual", palette = 2)
    
ggsave(filename = "../../figures/plots/points_accuracy_continuous.pdf",
       width = 7,
       height = 4)
```
## Accuracy with age (continuous)

```{r fig.height=4, fig.width=7}
set.seed(1)

df.plot.individual = df.choices %>% 
    # add continuous age
    left_join(df.data %>% 
                  select(participant, age_cts),
              by = "participant") %>% 
    group_by(participant, age, age_cts) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    ungroup() %>% 
    mutate(age = factor(age, levels = c(3:8,
                                        "adult\nvision",
                                        "adult\nvision & sound")))

df.plot.means = df.choices %>% 
    mutate(age = as.character(age)) %>% 
    group_by(participant, age) %>% 
    summarize(pct_correct = sum(correct)/n()) %>% 
    bind_rows(df.adults %>% 
                  mutate(correct = answer == ground_truth,
                         age = "adult") %>% 
                  group_by(participant, experiment, age) %>% 
                  summarize(pct_correct = sum(correct)/n()) %>% 
                  mutate(age = str_c(age,"\n", experiment),
                         age = str_replace(age, "_", " & "))) %>% 
    group_by(age) %>% 
    summarize(response = Hmisc::smean.cl.boot(pct_correct),
              n = n()) %>% 
    mutate(index = c("mean", "low", "high")) %>% 
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
    left_join(df.choices %>% 
                  left_join(df.data %>% 
                                select(participant, age_cts),
                            by = "participant") %>% 
                  distinct(participant, age, age_cts) %>% 
                  group_by(age) %>% 
                  summarize(age_mean = mean(age_cts)) %>% 
                  mutate(age = as.character(age)),
              by = "age") %>% 
    mutate(age_mean = ifelse(age == "adult\nvision", 10, age_mean),
           age_mean = ifelse(age == "adult\nvision & sound", 11, age_mean),
           age = factor(age, levels = c(3:8, "adult\nvision", "adult\nvision & sound")))

df.text = df.plot.means %>% 
    select(age, age_mean, n) %>% 
    mutate(label = n,
           label = ifelse(age == "3", str_c("n = ", n), n),
           y = 0.95)

ggplot() + 
    geom_hline(yintercept = seq(0, 1, 0.1),
               linetype = 1,
               alpha = 0.1) + 
    geom_hline(yintercept = 1/3,
               linetype = 2,
               color = "gray50") + 
    geom_point(data = df.plot.individual,
               mapping = aes(x = age_cts,
                             y = pct_correct,
                             color = age),
               show.legend = F,
               size = 1) +
    geom_pointrange(data = df.plot.means,
                    mapping = aes(x = age_mean,
                                  y = mean,
                                  ymin = low,
                                  ymax = high,
                                  fill = age),
                    shape = 21,
                    size = 1,
                    show.legend = F) +
    geom_text(data = df.text,
              mapping = aes(x = age_mean,
                            y = y,
                            label = label),
              size = 6,
              color = "gray20") +
    labs(x = "age (in years)",
         y = "% correct") +
    coord_cartesian(ylim = c(0, 1)) + 
    scale_x_continuous(breaks = c(seq(3, 9, 1), 10:11),
                       labels = c(seq(3, 9, 1), "adult\nvision", "adult\nvision & sound"),
                       expand = expansion(add = c(0.2, 1))) + 
    scale_y_continuous(breaks = seq(0, 1, 0.2),
                       labels = str_c(seq(0, 1, 0.2) * 100, "%"),
                       expand = expansion(add = c(0, 0.05))) + 
    scale_fill_brewer(type = "qual", palette = 2) +
    scale_color_brewer(type = "qual", palette = 2) + 
    theme(axis.text.x = element_text(size = 14))
    
ggsave(filename = "../../figures/plots/points_accuracy_continuous.pdf",
       width = 10,
       height = 4)
```


## Model fits 

### Children

#### Per participant 

```{r fig.height=5, fig.width=10, echo=FALSE}
# model_selection = c("baseline", "matching", "vision", "both")
model_selection = c("baseline", "matching", "vision", "both")

df.plot = df.fits %>% 
    group_by(age) %>% 
    # arrange(age,
    #         desc(baseline),
    #         matching,
    #         adult_vision,
    #         adult_vision_sound) %>% 
    arrange(age,
            desc(baseline),
            matching,
            vision,
            both) %>%
    ungroup() %>% 
    mutate(participant_index = 1:n()) %>%
    pivot_longer(cols = -c(age, participant, participant_index)) %>% 
    mutate(participant_index = as.factor(participant_index),
           age = str_c(age, " years"),
           name = factor(name,
                       levels = model_selection,
                       labels = c("guessing", "matching",
                                  "simulation (vision)","simulation (vision & sound)")))

ggplot(data = df.plot,
       mapping = aes(x = participant_index,
                     y = value,
                     # fill = fct_rev(name))) + 
                     fill = name)) + 
    geom_bar(stat = "identity",
             color = "black",
             position = position_stack(reverse = TRUE)) + 
    facet_wrap(~ age,
               scales = "free_x") + 
    scale_fill_brewer(palette = "Set1") + 
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = str_c(seq(0, 100, 25), "%"),
                       expand = expansion(add = c(0, 0.01))) + 
    labs(y = "posterior over models",
         fill = "model") + 
    theme(axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 14),
          axis.title.x = element_blank(),
          legend.position = "bottom",
          legend.text = element_text(size = 16)
          # axis.text.x = element_blank() 
          ) #+ 
    # guides(fill = guide_legend(reverse=TRUE))

# ggsave(filename = "../../figures/plots/bars_individual_children.pdf",
ggsave(filename = "../../figures/plots/bars_individual_model.pdf",
       width = 12,
       height = 6)
```

#### Per age group

```{r fig.height=4, fig.width=10, echo=FALSE}
model_selection = c("baseline", "matching",
                    "vision","both")

df.plot = df.fits %>% 
  group_by(age) %>% 
  summarize(across(all_of(model_selection), ~ mean(.))) %>% 
  ungroup() %>% 
  pivot_longer(cols = -age) %>% 
  mutate(age = str_c(age, " years"),
         name = factor(name,
                       levels = model_selection,
                       labels = c("guessing", "matching",
                                  "vision","vision & sound")))
df.text = df.fits %>% 
  count(age) %>% 
  mutate(label = str_c("n = ", n),
         age = str_c(age, " years"),
         value = 1.03,
         name = NA)

ggplot(data = df.plot,
       mapping = aes(x = age,
                     y = value,
                     fill = name)) + 
    geom_bar(position = position_stack(reverse = TRUE),
             stat = "identity",
             color = "black") + 
    geom_text(data = df.text,
              mapping = aes(label = label),
              size = 6) +
    scale_fill_brewer(palette = "Set1") + 
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = str_c(seq(0, 100, 25), "%"),
                       expand = expansion(add = c(0, 0.02))) + 
    labs(y = "posterior over models",
         fill = "model") + 
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(size = 16),
          legend.text = element_text(size = 16),
          legend.position = "bottom")
# guides(fill = guide_legend(reverse=TRUE))

# ggsave(filename = "../../figures/plots/bars_overall_children.pdf",
# ggsave(filename = "../../figures/plots/bars_overall_model.pdf",
#        width = 10,
#        height = 6)
```

#### Per age group (with adults)

```{r fig.height=4, fig.width=10, echo=FALSE}
model_selection = c("baseline", "matching", "vision","both")

df.data = df.fits %>% 
    mutate(age = str_c(age, " years")) %>% 
    bind_rows(df.fits.adults %>% 
                  mutate(experiment = str_replace(experiment, "_", " & "),
                         age = str_c("adult\n", experiment)) %>% 
                  select(-experiment)) %>% 
    mutate(age = factor(age, levels = c("3 years", "4 years", "5 years", 
                                        "6 years", "7 years", "8 years", 
                                        "adult\nvision", "adult\nvision & sound")))

df.plot = df.data %>% 
  group_by(age) %>% 
  summarize(across(all_of(model_selection), ~ mean(.))) %>% 
  ungroup() %>% 
  pivot_longer(cols = -age) %>% 
  mutate(name = factor(name,
                       levels = model_selection,
                       labels = c("guessing", "matching",
                                  "simulation (vision)","simulation (vision & sound)")))

df.text = df.data %>%
    count(age) %>%
    mutate(label = str_c("n = ", n),
           value = 1.03) %>% 
    ungroup() %>% 
    mutate(x = c(1:6, 7.5, 8.5))

df.plot = df.plot %>% 
    mutate(x = c(rep(1:6, each = 4), rep(c(7.5, 8.5), each = 4)))

ggplot(data = df.plot,
       mapping = aes(x = x,
                     y = value)) + 
    geom_bar(mapping = aes(fill = name),
             position = position_stack(reverse = TRUE),
             stat = "identity",
             color = "black") + 
    geom_text(data = df.text,
              mapping = aes(label = label),
              size = 6) +
    scale_fill_brewer(palette = "Set1") + 
    scale_x_continuous(breaks = c(1:6, 7.5, 8.5),
                       labels = levels(df.plot$age)) +
    scale_y_continuous(breaks = seq(0, 1, 0.25),
                       labels = str_c(seq(0, 100, 25), "%"),
                       expand = expansion(add = c(0, 0.02))) + 
    labs(y = "posterior over models",
         fill = "model") + 
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(size = 16),
          axis.text.x = element_text(size = 16),
          legend.text = element_text(size = 16),
          legend.position = "bottom")
# guides(fill = guide_legend(reverse=TRUE))

ggsave(filename = "../../figures/plots/bars_overall_children.pdf",
# ggsave(filename = "../../figures/plots/bars_overall_model.pdf",
       width = 12,
       height = 6)
```


### Adults 

#### Per participant 

```{r fig.height=5, fig.width=20}
df.plot = df.fits.adults %>% 
  pivot_longer(cols = -c(experiment, participant)) %>% 
  mutate(participant = as.factor(participant),
         name = factor(name,
                       # levels = c("baseline", "matching",
                       #            "adult_vision","adult_vision_sound"),
                       levels = c("baseline", "matching",
                                  "vision","both"),
                       labels = c("baseline", "matching",
                                  "vision","vision & sound")))
ggplot(data = df.plot,
       mapping = aes(x = participant,
                     y = value,
                     fill = name)) + 
  geom_bar(position = "stack",
           stat = "identity",
           color = "black") + 
  facet_wrap(~ experiment,
             scales = "free_x") + 
  scale_fill_brewer(palette = "Set1") + 
  labs(y = "% of each model") + 
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10))
```

#### Per experiment 

```{r}
df.plot = df.fits.adults %>% 
  group_by(experiment) %>% 
  summarize(across(all_of(model_selection), ~ mean(.))) %>% 
  ungroup() %>% 
  pivot_longer(cols = -experiment) %>% 
  mutate(name = factor(name,
                       # levels = c("baseline", "matching",
                       #            "adult_vision","adult_vision_sound"),
                       levels = c("baseline", "matching",
                                  "vision","both"),
                       labels = c("baseline", "matching",
                                  "vision","vision & sound")))
ggplot(data = df.plot,
       mapping = aes(x = experiment,
                     y = value,
                     fill = name)) + 
  geom_bar(position = "stack",
           stat = "identity",
           color = "black") + 
  scale_fill_brewer(palette = "Set1") + 
  labs(y = "% of each model") + 
  theme(axis.text.y = element_blank(),
        axis.title.x = element_blank())
```


## Correct responses per world 

```{r echo=FALSE, fig.height=6, fig.width=12}
df.plot = df.choices %>% 
  mutate(response = factor(correct,
                          levels = c(0, 1),
                          labels = c("wrong", "correct")))

ggplot(data = df.plot,
       mapping = aes(x = reorder(world, correct),
                     fill = response)) +
  geom_bar(position = "stack",
           color = "black") +
  coord_flip(expand = F) +
  labs(x = "world",
       y = "number of responses") + 
  scale_fill_brewer(palette = "Set1") + 
  theme(legend.position = "bottom") + 
  guides(fill = guide_legend(reverse = T))

#ggsave("../../figures/plots/bars.pdf",
       #width = 8,
       #height = 6)
```

## Correct responses per participant

```{r echo=FALSE, fig.height=8, fig.width=8}
df.plot = df.choices %>% 
  mutate(participant = as.factor(participant))

ggplot(data = df.plot,
       mapping = aes(x = participant, 
                     y = correct,
                     fill = age)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               show.legend = F,
               color = "black") + 
  geom_hline(yintercept = 1/3,
             linetype = 2) + 
  facet_grid(~ age,
             scales = "free_x") + 
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = seq(0, 100, 25),
                     limits = c(0, 1),
                     expand = expansion(add = c(0, 0))) +
  theme(axis.text.x = element_blank())
```

## Proportion of correct responses over time 

```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
df.plot = df.choices %>% 
  mutate(trial = as.factor(trial))

ggplot(data = df.plot,
       mapping = aes(x = trial, 
                     y = correct)) + 
  geom_hline(yintercept = 1/3,
             linetype = 2) + 
  stat_summary(fun.data = mean_cl_boot) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = seq(0, 100, 25),
                     limits = c(0, 1))
```

## Overall accuracy 



# Session Info 

```{r, echo=FALSE}
sessionInfo()
```

# Scratch pad 

```{r}
df.predictions %>% 
    select(world, baseline, matching, vision, both) %>% 
    filter(world == 35)
    
```




